Expanding the scope of experimental archaeology using the Perception-Process-Product analytical framework

### 2022-12-06 manuscript/manuscript.Rmd
added a few more references.

This part talks about the goal and toolbox of PPP framework, which is understanding the multi-level understanding of variation. the first two p captures different level of variation

Traditionally, experimental archaeology focuses on generating knowledge regarding the causal mechanism at behavioral level to explain the variation of material culture [@eren2016]. In the past decades, actualistical experiments becomes more common [@liu2022].

@@

The PPP analytical framework inherently advocate an collaborative mode of knowledge production [@ranhorn2020].

>>>>

This part talks about the goal and toolbox of PPP framework, which is understanding the multi-level understanding of variation. the first two p captures different level of variation: EQUIFINALITY [@chami2015].

Is RCT the golden standard of knowledge [@cartwright2007]

Traditionally, experimental archaeology focuses on generating knowledge regarding the causal mechanism at behavioral level to explain the variation of material culture [@eren2016]. In the past decades, actualistical experiments becomes more common [@liu2022]. new toolkit such as BORIS were introduced [@friard2016]

@@

The PPP analytical framework inherently adopts an collaborative mode of knowledge production, which has been advocated in experimental studies [@ranhorn2020] and museum collection studies [@timbrell2022].

# Open science beyond reproducibility

The last step is uploading the data to a open-access repository [@marwick2017]. The building of manufacture can cost.
